Data Responsive-report

### 2021-02-08 GALI_2020.Rmd
exploring plots

##Function to extract summary model tables  
```{r}
lmOut <- function(res, file="test.csv", ndigit=3, writecsv=T) {
  if (length(grep('summary', class(res)))==0) res <- summary(res)
  co <- res$coefficients
  nvar <- nrow(co)
  ncoll <- ncol(co)
  f <- res$fstatistic
  formatter <- function(x) format(round(x,ndigit),nsmall=ndigit)
  # This sets the number of rows before we start recording the coefficients
  nstats <- 4
  # G matrix stores data for output
  G <- matrix("", nrow=nvar+nstats, ncol=ncoll+1)
  G[1,1] <- toString(res$call)
  # Save rownames and colnames
  G[(nstats+1):(nvar+nstats),1] <- rownames(co)
  G[nstats, 2:(ncoll+1)] <- colnames(co)
  # Save Coefficients
  G[(nstats+1):(nvar+nstats), 2:(ncoll+1)] <- formatter(co)
  # Save F-stat
  G[1,2] <- paste0("F(",f[2],",",f[3],")")
  G[2,2] <- formatter(f[1])
  # Save F-p value
  G[1,3] <- "Prob > P"
  G[2,3] <- formatter(1-pf(f[1],f[2],f[3]))
  # Save R2
  G[1,4] <- "R-Squared"
  G[2,4] <- formatter(res$r.squared)
  # Save Adj-R2
  G[1,5] <- "Adj-R2"
  G[2,5] <- formatter(res$adj.r.squared)
  print(G)
  if (writecsv) write.csv(G, file=file, row.names=F)
}

@@

#Exploring with plots
```{r}
ggplot(gali_joined, aes()) +

>>>>

@@

#Exploring with plots
```{r}
ggplot(gali_joined, aes(inst_hc_gem,inst_fc_gem)) +
  geom_point()
